Typechecking a linear \picalc

### 2020-02-07 paper/paper.tex
Some initial notes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Machine verification of typed process calculi}
\subtitle{Research Proposal}
\author{Uma Zalakain}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\cite{empty}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Typechecking a linear \picalc}
\author{Uma Zalakain}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
  We present the syntax, operational semantics, and typing rules for a \picalc{} with linear and shared types. We use a typing with leftovers approach \cite{} to encode our typing rules. We build framing and weakening proofs that we then use to prove subject congruence and subject reduction.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Goals: present nice model, prove subject reduction

Intensional (correct by construction) vs extensional

same syntax and semantics, different typing rules

full formalisation available in Agda

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related work}

\cite{previous-work} polymorphic tokens, HOAS

\cite{typing-with-leftovers}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Syntax}

variable references (strings, locally named, de Bruijn)

strings to maybe de Bruijn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Semantics}

keeping track of the variable on which communication occurs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Linear typing rules}

using dependent types to encode typing rules

removing from context vs keeping in context but marking it used

two-layered approach: types on one hand, capabilities on the other

n multiplicities as a generalisation

properties of the underlaying monoid

nat numbers + omega as a generalisation

partial vs total

\subsection{Typing with leftovers}

Variable references as proofs of capability

Context splits at each variable reference

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Subject reduction}

\subsection{Framing}
\subsection{Weakening}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future work}

Work that will be done time permiting:

Decidable typechecking

Proof of progress

Product types

Sum types

Encoding of session types
